Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
edits Sec 5

%% %-------------------------------
%% \section{Related Work}
%% \label{sec:rw}
%% %-------------------------------

%-------------------------------
\section{Conclusions}
%-------------------------------

We have presented two automated approaches to synthesize digital state-feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the closed-loop model dynamics 
up to a completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
%
Both approaches are novel within the control literature: they put 
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering various error sources in the implementation 
of the digital control algorithm and in the computational modeling of plant dynamics. 
%
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks , which have been derived from the control literature.

Future work will focus the extension of these approaches to the continuous time case, 
to models with output-based control architectures (hinging on the use of observers), 
and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

>>>>

%-------------------------------
\section{Conclusion}
%-------------------------------

We have presented two automated approaches to synthesize digital
state-feedback controllers that ensure both stability and safety over the
state-space representation.  The first approach relies on explicit unfolding
of the closed-loop model dynamics up to a completeness threshold, whilst the
second one applies abstraction refinement and acceleration to increase speed
whilst retaining soundness.
%
Both approaches are novel within the control literature: they give a fully
automated synthesis method that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant dynamics.
%
Our experimental results show that both approaches are able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  In particular, both approaches complement each other
and together solve all benchmarks, which have been derived from the control
literature.

Future work will focus the extension of these approaches to the
continuous-time case, to models with output-based control architectures
(hinging on the use of observers), and to considering performance
requirements (alongside safety) in the synthesis of digital controllers.
